Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-22 tex/results.tex
minor edits, results section

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
When the resonance peaks are sharp and narrow, the wavelengths at which they occur in the scattering and absorption spectra are nearly the same.
For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are close \cite{wiley-etal-2006}.  
Since silicon carbide has more pronounced peaks than silver, the wavelength at which they occur in the extinction and scattering spectra are more closely aligned.

@@

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. 
We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
With that experience, and given the difficulty caused by sharp edges, we are content with studying grid-independence here instead.
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
 to 19,200 triangles (density $1.11\times10^{-5}$ $\text{\AA}$ squared):
 the computed results show no discernible difference.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak located at $\approx$ 10.6 $\mu$m  is much diminished in the green curve for both the $E\parallel b$  the $E\parallel a$ plots. 
These effects can be attributed 
to the effect of the roundness. This is consistent with the results in Rockstuhl et al.

@@

Our first aim was to replicate the computational result presented in Figure S4 of their supplementary 
material, corresponding to the black curve on their plot. In this 
figure, they show simulation results for the resonance spectral position of the lower-frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times larger than in the other cases), diminishing the effects of coupling, which makes it 
a better candidate to replicate using \pygbe. 
In our calculations, the setup consists of a single pillar, with no substrate.
Our second attempted replication is  
for the results presented in Figure 2a, corresponding to reflectance measurements across wave number
for pillars with aspect ratio $AR=4$, angle of incidence of 22 degrees, and incoming polarization parallel to the 
length of the pillars. For this case, the authors also reported experimental results that we will use for validation of our solver.

@@

\paragraph{Method:}
Ellis et al.\ ran experiments using reflectance spectroscopy and they computed the solution of
Maxwell's equations via the RF package of the finite element solver in the commercial software COMSOL. 
In their simulations, 
they used one pillar over a portion of substrate, with periodic boundary conditions to represent an array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in this case 
since the pillar's size is small compared to the wavelengths involved in the simulations: 
which are in the range 10000--12500 nm. 
We measure extinction cross section, which will express as peaks instead of dips (shown in the reflection plots of Ellis et al.). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a mesh density of $\approx \; 1.7 \times10^{-5}$ triangles per $\text{\AA}$ squared to create the meshes for 
the aspect ratio variation study.

@@

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross section $C_{ext}$ across the wave numbers in the range
800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations where performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that it is not a longitudinal one and extracted its wavelength (see \ref{tab:ar_peaks}) to replicate 
\ref{fig:rep_FS4_ellis}. Figure \ref{fig:rep_FS4_ellis} shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

@@

The results of Figure 2a in Ellis et al.\ were obtained on a pillar of aspect ratio $AR=4$. For this case,
we have the original mesh, provided to us by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on their paper), as well 
as to replicate their simulations (green curve on their paper).
Figure 2a of Ellis et al., presents measured and simulated reflectances of SiC pillar
arrays with a 500 nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe, we computed the extinction-cross section of an isolated SiC pillar ($AR=4$)
with no substrate, submerged in air under a constant electric field in the $z$-direction, 
and rotated the orientation of the pillar to match the angle of incidence used by Ellis et al.\ (see Figure \ref{fig:ellis_ang_inc}).
In Figure \ref{fig:pygbe_vs_exp_2a}, we present a 
comparison of our simulations and the experimental results of Ellis et al. A 
difference in the wavelengths of the peaks is noticeable. This may be attributed to the
fact that in their experiments the separation between pillars is of 500 nm, which implies
there are coupling effects that in our simulations are not considered.

>>>>

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not generally comparable. 
When the resonance peaks are sharp and narrow, however, the wavelengths at which they occur in the scattering and absorption spectra are nearly the same.
For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are close \cite{wiley-etal-2006}.  
Since silicon carbide has more pronounced peaks than silver, the wavelength at which they occur in the extinction and scattering spectra are more closely aligned.

@@

We performed a grid-independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the $z$-axis (a similar setup to the square cylinder on Fig. 18 of 
Rockstuhl et al.\cite{rockstuhl2005}). 
Due to the nature of the geometry and its sharp edges, it was challenging to see proper convergence. 
We have completed grid-convergence analysis for this type of physics in a previous work, but using spherical geometries \cite{ClementiETal2019}. 
With that experience, and given the difficulty caused by sharp edges, we are content with studying grid-independence here instead.
Figure \ref{fig:cube535} shows the grid-independence study, using meshes with  15,552 triangles (density $9.05\times10^{-4}$ per $\text{\AA}$ squared)
 to 19,200 triangles (density $1.11\times10^{-5}$ per $\text{\AA}$ squared):
 the computed results show no discernible difference.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak located at $\approx$ 10.6 $\mu$m  is much diminished in the green curve for both the $E\parallel b$  the $E\parallel a$ plots. 
These effects can be attributed 
to the roundness, consistent with the results in Rockstuhl et al.

@@

Our first aim was to replicate the computational result presented in Figure S4 of their supplementary 
material, corresponding to the black curve on their plot. In this 
figure, they show simulation results for the resonance spectral position of the lower-frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22 degrees.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times larger than in the other cases), diminishing the effects of coupling, which makes it 
a better candidate to replicate using \pygbe. 
In our calculations, the setup consists of a single pillar, with no substrate.
Our second attempted replication is  
for the results presented in Figure 2a, corresponding to reflectance measurements across wave number
for pillars with aspect ratio $AR=4$, angle of incidence 22 degrees, and incoming polarization parallel to the 
length of the pillars. For this case, the authors also reported experimental results that we will use for validation of our solver.

@@

\paragraph{Method:}
Ellis et al.\ ran experiments using reflectance spectroscopy and they computed the solution of
Maxwell's equations via the RF package of the finite element solver in the commercial software COMSOL. 
In their simulations, 
they used one pillar over a portion of substrate, with periodic boundary conditions to represent an array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in this case 
since the pillar's size is small compared to the wavelengths involved in the simulations: 
in the range 10000--12500 nm. 
We measured extinction cross section, which will express as peaks instead of dips (shown in the reflection plots of Ellis et al.). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (quantity of interest) at which these events happen.

\paragraph{Mesh:}
For the case with aspect ratio $AR=4$, we have a non-uniform triangular surface mesh ($N=4398$) provided to us by the authors of 
Ellis et al., which we used for validation and replication of Figure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material, we needed the remaining aspect ratio meshes. We generated uniform meshes using our
Python script, and we determined the density of these meshes by comparing the extinction cross-section for the case with $AR=4$ of 
our mesh and the one provided by Ellis et al. We noticed that using around double the number of elements ($N=8564$) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross-section were, on average, smaller than 3$\%$, and the variation on the wavelength peak
position was smaller than 1 cm$^{-1}$. This analysis led us to a density of $\approx \; 1.7 \times10^{-5}$ triangles per $\text{\AA}$ squared to create the meshes for 
the aspect ratio variation study.

@@

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross-section $C_{ext}$ across the wave numbers in the range
800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations where performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that is not a longitudinal one and extracted its wavelength (see Table \ref{tab:ar_peaks}) to replicate 
Figure \ref{fig:rep_FS4_ellis}. This figure shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

@@

The results of Figure 2a in Ellis et al.\ were obtained on a pillar of aspect ratio $AR=4$. For this case,
we have the original mesh, provided to us by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on their paper), as well 
as to replicate their simulations (green curve on their paper).
Figure 2a of Ellis et al.\ presents measured and simulated reflectances of SiC pillar
arrays with a 500-nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe, we computed the extinction-cross section of an isolated SiC pillar ($AR=4$)
with no substrate, submerged in air under a constant electric field in the $z$-direction, 
and rotated the orientation of the pillar to match the angle of incidence used by Ellis et al.\ (see Figure \ref{fig:ellis_ang_inc}).
In Figure \ref{fig:pygbe_vs_exp_2a}, we present a 
comparison of our simulations and the experimental results of Ellis et al. A 
difference in the wavelengths of the peaks is noticeable. This may be attributed to the
fact that in their experiments the separation between pillars is 500 nm, which implies
there are coupling effects that in our simulations are not considered.
